### 2024-08-29 Scripts/Manuscript/manuscript.Rmd
implemented code review suggested changes

### Measurement Reporting
This study aims to conceptually replicate the findings on measurement reporting of @flake2022construct. To do so we evaluate how common QMPs are in replications of psychological research (RQ4a) and original psychological research (RQ4b).

@@

This manuscript was created in RStudio [*v`r rstudioapi::versionInfo()$version`*\;@R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [*v`r getNamespaceVersion("worcs")[[1]]`*\; @vanlissaWORCS2021] to ensure reproducibility and transparency. All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/>.

@@

To be included in the planned analyses on calculated reliabilities (RQ1, RQ2, and RQ3), the measure had to be a scale consisting of multiple items. If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended (e.g. no reverse-coded items). Pilot data were omitted from the analyses. These criteria resulted in suitable item score data from `r apa_num(nrow(data_h3_avg))` replication sets spread across on average approximately `r apa_num(mean(table(data_h3_multiple$g)), digits = 0)` lab locations for the analyses of Hypotheses 2 & 3.

```{r CleaningReplicationDatasetsData, include = FALSE, eval = FALSE}
##### Data already available, code does not need to be run!
### ML 1
# 1.3
data_1.3_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[22:29])
colnames(data_1.3_clean)[1] <- "g"
# 1.10
data_1.10_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[108:115])
colnames(data_1.10_clean)[1] <- "g"
# 1.11
data_1.11_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[73:76])
colnames(data_1.11_clean)[1] <- "g"
# 1.12.1
# not found
# 1.12.3
data_1.12.3.1_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[54:59])
colnames(data_1.12.3.1_clean)[1] <- "g"
data_1.12.3.2_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[60:65])
colnames(data_1.12.3.2_clean)[1] <- "g"

### ML 2
# 2.2
data_2.2_clean <- cbind(as.factor(data_2.2[[5]]), data_2.2[6:11])
colnames(data_2.2_clean)[1] <- "g"
# 2.3
# data does not appear suitable
# 2.4.1
data_2.4.1_clean <- cbind(as.factor(data_2.4.1[[5]]), data_2.4.1[6:11])
colnames(data_2.4.1_clean)[1] <- "g"
# 2.4.2
data_2.4.2_clean <- cbind(as.factor(data_2.4.2[[5]]), data_2.4.2[6:14])
colnames(data_2.4.2_clean)[1] <- "g"
# 2.8.2
data_2.8.2_clean <- cbind(as.factor(data_2.8.2[[6]]), data_2.8.2[9:13])
colnames(data_2.8.2_clean)[1] <- "g"
# 2.10.1
data_2.10.1_clean <- cbind(as.factor(data_2.10.1[[5]]), data_2.10.1[6:11])
colnames(data_2.10.1_clean)[1] <- "g"
# 2.12.1
data_2.12.1_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(6,7,8,9,10,31,32,33,34,35)]) 
data_2.12.1_clean[3465:6905,2:6] <- data_2.12.1_clean[3465:6905,7:11]
data_2.12.1_clean <- data_2.12.1_clean[1:6]
colnames(data_2.12.1_clean)[1] <- "g"
# 2.12.2
data_2.12.2_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(11,14,15,18,19,22,24,27,28,29,36,39,40,43,44,47,49,52,53,54)]) 
data_2.12.2_clean[3465:6905,2:11] <- data_2.12.2_clean[3465:6905,12:21]
data_2.12.2_clean <- data_2.12.2_clean[1:11]
colnames(data_2.12.2_clean)[1] <- "g"
# 2.12.3
data_2.12.3_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(12,13,16,17,20,21,23,25,26,30,37,38,41,42,45,46,48,50,51,55)]) 
data_2.12.3_clean[3465:6905,2:11] <- data_2.12.3_clean[3465:6905,12:21]
data_2.12.3_clean <- data_2.12.3_clean[1:11]
colnames(data_2.12.3_clean)[1] <- "g"
# 2.15
data_2.15_clean <- cbind(as.factor(data_2.15[[5]]), data_2.15[8:12])
colnames(data_2.15_clean)[1] <- "g"
# 2.19.1
# difficult to extract
# 2.19.2
# difficult to extract
# 2.20
data_2.20_clean <- cbind(as.factor(data_2.20[[5]]), data_2.20[6:45]) 
data_2.20_clean[3729:7396,2:21] <- data_2.20_clean[3729:7396,22:41]
data_2.20_clean <- data_2.20_clean[1:21] 
# coding so all 1's means somebody used rule-based grouping strategy
data_2.20_clean[,c(2, 4, 6, 8, 10, 12, 14, 16, 18, 20)] <- ifelse(data_2.20_clean[,c(2, 4, 6, 8, 10, 12, 14, 16, 18, 20)] == 1, 1, 0)
data_2.20_clean[,c(3, 5, 7, 9, 11, 13, 15, 17, 19, 21)] <- ifelse(data_2.20_clean[,c(3, 5, 7, 9, 11, 13, 15, 17, 19, 21)] == 2, 1, 0)
colnames(data_2.20_clean)[1] <- "g"
# 2.23
data_2.23_clean <- cbind(as.factor(data_2.23[[5]]), data_2.23[c(7,8,12,13,15)])
colnames(data_2.23_clean)[1] <- "g"

### ML 3
# 3.2.1
data_3.2.1 <- cbind(as.factor(data_ml3[[1]]), data_ml3[77:86] - 1)
data_3.2.1.1_clean <- na.omit(data_3.2.1[1:6])
colnames(data_3.2.1.1_clean)[1] <- "g"
data_3.2.1.2_clean <- na.omit(data_3.2.1[c(1, 7:11)])
colnames(data_3.2.1.2_clean)[1] <- "g"
# 3.5
# data appears unusable
# 3.7.1
data_3.7.1_clean <- na.omit(cbind(as.factor(data_ml3[[1]]), data_ml3[38:42]))
colnames(data_3.7.1_clean)[1] <- "g"
# 3.7.2
data_3.7.2_clean <- na.omit(cbind(as.factor(data_ml3[[1]]), data_ml3[89:94]))
colnames(data_3.7.2_clean)[1] <- "g"
# 3.8.1
# a single measure was reported
# 3.8.2
data_3.8.2_clean <- na.omit(cbind(as.factor(data_ml3[[1]]), data_ml3[29:30])) 
colnames(data_3.8.2_clean)[1] <- "g"

### ML 5
# 5.1.1
data_5.1.1_clean <- cbind(as.factor(data_5.1[[2]]), data_5.1[13:27])
colnames(data_5.1.1_clean)[1] <- "g"
# 5.1.2
data_5.1.2_clean <- cbind(as.factor(data_5.1[[2]]), data_5.1[28:33])
colnames(data_5.1.2_clean)[1] <- "g"
# 5.4
data_5.4_clean <- cbind(as.factor(data_5.4[[1]]), data_5.4[18:41])
colnames(data_5.4_clean)[1] <- "g"
# 5.5.1 & 5.5.2
# from this dataset it appears that this data will be difficult to use.
# 5.5.2
# also difficult to use
# 5.7 
data_5.7_clean <- cbind(as.factor(data_5.7[[3]]), data_5.7[c(25, 34, 35, 36, 37, 38, 39, 40, 41, 42)])
colnames(data_5.7_clean)[1] <- "g"
# 5.9.1
data_5.9.1_clean <- na.omit(cbind(as.factor(data_5.9.1[[4]]), data_5.9.1[c(79, 83, 87, 91, 95, 98, 101)]))
colnames(data_5.9.1_clean)[1] <- "g"

### to summarize
# total number of likely usable: 15 (1.10, 1.11, 1.12.3.1, 1.12.3.2, 2.10.1, 
# 2.12.1, 2.12.2, 2.12.3, 2.15, 2.23, 3.7.1, 3.7.2, 3.8.2, 5.7, 5.9.1)
# total number of maybe usable: 6 (1.3, 2.20, 3.2.1.1, 3.2.1.2, 5.1.1, 5.4)
# total alpha coefficient comparison usable: 3 
#                                           1.11: 0.82
#                                           3.7.2: 0.67
#                                           5.9.1: 0.84

@@

```{r CleaningCodedData, include = FALSE, eval = FALSE}
##### Data already available, code does not need to be run!
# Selecting the relevant rows and columns for the data
coded_data_initial_sel <- coded_data_initial_raw[3:160, 18:57]
coded_data_revised_sel <- coded_data_revised_raw[3:160, 18:38]
coded_data_vignette_raw <- coded_data_vignette_raw[3:160, 2]

@@

```{r FinalPreparationData, include = FALSE, eval = FALSE}
##### Data already available, code does not need to be run
### this code prepares the various pieces of data to be ready to use for the 
### analyses.
## confirmatory analyses
# for hypothesis 4
data_h4 <- data_prep_H4(coded_data_original_shortened, coded_data_replications)
# for hypothesis 5
data_h5 <- data_prep_H5(coded_data_replications)
# for hypothesis 6
data_h6 <- data_prep_H6(coded_data_original_shortened, coded_data_replications)

# for hypothesis 1
data_h1 <- data_prep_H1(coded_data_original_shortened, coded_data_replications)
# for hypothesis 2
data_h2 <- data_prep_H2(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, data_1.12.3.2_clean, data_2.12.1_clean, data_2.12.2_clean, data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.1_clean, data_3.7.2_clean, data_3.8.2_clean, data_5.1.1_clean, data_5.1.2_clean, data_5.7_clean, data_5.9.1_clean)
# for hypothesis 3
data_h3_multiple <- Data_prep_H3_multiple(coded_data_replications, data_h2)
data_h3_avg <- Data_prep_H3_avg(coded_data_replications, data_h3_multiple)

## graphs
# plot accompanying the results for Hypotheses 4, 5, & 6.
plot_456_data <- data_prep_plot_456(data_h6)
# plot accompanying the results for Hypotheses 4, & 6
plot_46_data <- data_prep_plot_46(data_h6[c(3, 6, 9, 12, 15, 18, 36, 39, 42, 45, 48, 51)])
plot_46_data_rev <- data_prep_plot_46(data_h6[c(3, 21, 24, 27, 30, 33, 36, 54, 57, 60, 63, 66)])
# plot accompanying the results for Hypotheses 2, & 3
plot_23_data_alpha <- data_prep_plot_23_alpha(data_h3_multiple)
plot_23_data_omega <- data_prep_plot_23_omega(data_h3_multiple)
plot_23_data_reported_alpha <- data_prep_plot_23_alpha_reported(coded_data_original_shortened, data_h3_avg, data_h3_multiple)

### Exporting the final datasets for the analyses
# the open data
open_data(data = data_h4, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_h4))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_h4))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_h4))), ".yml"))

open_data(data = data_h6, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_h6))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_h6))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_h6))), ".yml"))

open_data(data = data_h5, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_h5))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_h5))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_h5))), ".yml"))

open_data(data = data_h1, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_h1))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_h1))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_h1))), ".yml"))

@@

open_data(data = data_h2, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_h2))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_h2))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_h2))), ".yml"))

open_data(data = data_h3_multiple, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_h3_multiple))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_h3_multiple))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_h3_multiple))), ".yml"))

open_data(data = data_h3_avg, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_h3_avg))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_h3_avg))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_h3_avg))), ".yml"))

@@

open_data(data = plot_23_data_reported_alpha, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(plot_23_data_reported_alpha))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(plot_23_data_reported_alpha))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(plot_23_data_reported_alpha))), ".yml")) 
```

@@

```{r ReplicationNrTable, warning = FALSE}
# construct the replication ratio table to be printed
replication_nr_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
                                      "N Total" = c(table(coded_data_replications$many_labs_version), nrow(coded_data_replications)), 
                                      "N Replicated" = c(table(coded_data_replications$many_labs_version, coded_data_replications$hypothesis_support)[, "Yes"], table(coded_data_replications$hypothesis_support)["Yes"]))

@@

Our data had a multilevel structure. Each replication was nested within one of four Many Labs projects. Furthermore, `r sum(coded_data_replications$appearance != 1)` replications used more than one primary measure, resulting in `r nrow(coded_data_replications)` measures in both `r sum(coded_data_replications$appearance == 1)` replications protocols and `r sum(coded_data_original$appearance == 1)` original articles[^2]. Of these `r nrow(coded_data_replications)` measures `r sum(coded_data_replications$mod_check == "True")` were modified from the original to the replication[^3]. In the replications, the data of responses on the measures was further nested in several labs per replication. The combined sample size of all labs in the replications was on average `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N), 0)` which was approximately `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N) / mean(coded_data_original_shortened[coded_data_original_shortened$appearance == 1 & !is.na(coded_data_original_shortened$N),]$N), 0)` times larger than the average in original studies, which were conducted in single labs.

@@

The average calculated Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h3_multiple$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$alpha, na.rm = TRUE), digits = 3)`. Figure \@ref(fig:Plot23AlphaCode) displays the distributions of the calculated Cronbach’s Alpha scores from each lab for each measure, separated by successful and unsuccessful replication.

```{r ReorderPlot23Data, warning = FALSE}
# data re-ordering (factor order was not saved in export)
plot_23_data_alpha_reordered <- data_prep_plot_23_alpha(plot_23_data_alpha)
```

@@

### use ggarange for aranging things at the side of this graph

@@

  # adding the blue triangles for reported reliability and green prediction intervals
  geom_point(data = plot_23_data_reported_alpha, mapping = aes(x = coefficient_reported, y = article_order), color = "blue", shape = 17, size = 3) +
  geom_point(mapping = aes(x = pi.lb), color = "green", shape = 124, size = 2.5) + 
  geom_point(mapping = aes(x = pi.ub), color = "green", shape = 124, size = 2.5) +

@@

```{r ReportedReliabiltiesRetrieval}
N_reported_reliabilities_original <- sum(coded_data_original_shortened$reliability_type != "Not Reported" & coded_data_original_shortened$reliability_type != "")

N_reported_reliabilities_replications <- apa_num(sum(coded_data_replications$reliability_type != "Not Reported" & coded_data_replications$reliability_type != ""), numerals = FALSE)

N_reported_reliabilities_replications_number_style <- apa_num(sum(coded_data_replications$reliability_type != "Not Reported" & coded_data_replications$reliability_type != ""))
```

@@

```{r Hypothesis3MainTest, include = FALSE}
## The main model to test hypothesis 3, through a logistic regression model.
H3_test_main_alpha <- glm(formula = replication ~ 1 + alpha, 
                                 family = binomial(), data = data_h3_avg)

@@

# well this OR is quite a ridiculous number..., but then again a step from 0 alpha to 1 is quite a jump too...
```

>>>>

This study aims to conceptually replicate the findings on measurement reporting of @flake2022construct. To do so we evaluate how common QMPs are in replications of psychological research (RQ4a) and original psychological research (RQ4b).

@@

This manuscript was created in RStudio [*v`r rstudioapi::versionInfo()$version`*\; @R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [*v`r getNamespaceVersion("worcs")[[1]]`*\; @vanlissaWORCS2021] to ensure reproducibility and transparency. All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/>.

@@

To be included in the planned analyses on calculated reliabilities (RQ1, RQ2, and RQ3), the measure had to be a scale consisting of multiple items. If cleaned data was available this was chosen over raw data, to ensure that variables were coded as intended (e.g. no reverse-coded items). Pilot data were omitted from the analyses. These criteria resulted in suitable item score data from `r apa_num(nrow(data_h23_avg))` replication sets spread across on average approximately `r apa_num(mean(table(data_h23$g)), digits = 0)` lab locations for the analyses of Hypotheses 2 & 3.

```{r CleaningReplicationDatasetsData, include = FALSE, eval = FALSE}
##### This code can be used to rerun the data preparation to convert the raw 
##### (input) data of the Many Labs replications into intermediate data.
##### However, because the intermediate data is also available in this project,
##### the manuscript can also be reproduced without running this code block.

### Below we extract the relevant data from the Many Labs' datasets. The first
### number in each dataset refers to the Many Labs project it is related to.
### The second number to which study the data is from in order of appearance in
### the Many Labs pre-registered protocols, or in the case of Many Labs 5, 
### within the OSF folder structure. If there is a third number, the study had 
### multiple relevant measures this refers to the order of appearance of the 
### measure where the data is from within the study's description in the Many 
### Labs protocol or OSF folder structure. A fourth number indicates which part
### of the data of this measure was taken, in case the measure assessed multiple
### constructs, as these were treated separately for some analyses.

## ML 1
# 1.3
data_1.3_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[22:29])
colnames(data_1.3_clean)[1] <- "g"
# 1.10
data_1.10_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[108:115])
colnames(data_1.10_clean)[1] <- "g"
# 1.11
data_1.11_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[73:76])
colnames(data_1.11_clean)[1] <- "g"
# 1.12.1
# not found
# 1.12.3
data_1.12.3.1_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[54:59])
colnames(data_1.12.3.1_clean)[1] <- "g"
data_1.12.3.2_clean <- cbind(as.factor(data_ml1[[5]]), data_ml1[60:65])
colnames(data_1.12.3.2_clean)[1] <- "g"

## ML 2
# 2.2
data_2.2_clean <- cbind(as.factor(data_2.2[[5]]), data_2.2[6:11])
colnames(data_2.2_clean)[1] <- "g"
# 2.3
# data does not appear suitable
# 2.4.1
data_2.4.1_clean <- cbind(as.factor(data_2.4.1[[5]]), data_2.4.1[6:11])
colnames(data_2.4.1_clean)[1] <- "g"
# 2.4.2
data_2.4.2_clean <- cbind(as.factor(data_2.4.2[[5]]), data_2.4.2[6:14])
colnames(data_2.4.2_clean)[1] <- "g"
# 2.8.2
data_2.8.2_clean <- cbind(as.factor(data_2.8.2[[6]]), data_2.8.2[9:13])
colnames(data_2.8.2_clean)[1] <- "g"
# 2.10.1
data_2.10.1_clean <- cbind(as.factor(data_2.10.1[[5]]), data_2.10.1[6:11])
colnames(data_2.10.1_clean)[1] <- "g"
# 2.12.1
data_2.12.1_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(6,7,8,9,10,31,32,33,34,35)]) 
data_2.12.1_clean[3465:6905,2:6] <- data_2.12.1_clean[3465:6905,7:11]
data_2.12.1_clean <- data_2.12.1_clean[1:6]
colnames(data_2.12.1_clean)[1] <- "g"
# 2.12.2
data_2.12.2_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(11,14,15,18,19,22,24,27,28,29,36,39,40,43,44,47,49,52,53,54)]) 
data_2.12.2_clean[3465:6905,2:11] <- data_2.12.2_clean[3465:6905,12:21]
data_2.12.2_clean <- data_2.12.2_clean[1:11]
colnames(data_2.12.2_clean)[1] <- "g"
# 2.12.3
data_2.12.3_clean <- cbind(as.factor(data_2.12[[5]]), data_2.12[c(12,13,16,17,20,21,23,25,26,30,37,38,41,42,45,46,48,50,51,55)]) 
data_2.12.3_clean[3465:6905,2:11] <- data_2.12.3_clean[3465:6905,12:21]
data_2.12.3_clean <- data_2.12.3_clean[1:11]
colnames(data_2.12.3_clean)[1] <- "g"
# 2.15
data_2.15_clean <- cbind(as.factor(data_2.15[[5]]), data_2.15[8:12])
colnames(data_2.15_clean)[1] <- "g"
# 2.19.1
# difficult to extract
# 2.19.2
# difficult to extract
# 2.20
data_2.20_clean <- cbind(as.factor(data_2.20[[5]]), data_2.20[6:45]) 
data_2.20_clean[3729:7396,2:21] <- data_2.20_clean[3729:7396,22:41]
data_2.20_clean <- data_2.20_clean[1:21] 
# coding so all 1's means somebody used rule-based grouping strategy
data_2.20_clean[,c(2, 4, 6, 8, 10, 12, 14, 16, 18, 20)] <- ifelse(data_2.20_clean[,c(2, 4, 6, 8, 10, 12, 14, 16, 18, 20)] == 1, 1, 0)
data_2.20_clean[,c(3, 5, 7, 9, 11, 13, 15, 17, 19, 21)] <- ifelse(data_2.20_clean[,c(3, 5, 7, 9, 11, 13, 15, 17, 19, 21)] == 2, 1, 0)
colnames(data_2.20_clean)[1] <- "g"
# 2.23
data_2.23_clean <- cbind(as.factor(data_2.23[[5]]), data_2.23[c(7,8,12,13,15)])
colnames(data_2.23_clean)[1] <- "g"

## ML 3
# 3.2.1
data_3.2.1 <- cbind(as.factor(data_ml3[[1]]), data_ml3[77:86] - 1)
data_3.2.1.1_clean <- na.omit(data_3.2.1[1:6])
colnames(data_3.2.1.1_clean)[1] <- "g"
data_3.2.1.2_clean <- na.omit(data_3.2.1[c(1, 7:11)])
colnames(data_3.2.1.2_clean)[1] <- "g"
# 3.5
# data appears unusable
# 3.7.1
data_3.7.1_clean <- na.omit(cbind(as.factor(data_ml3[[1]]), data_ml3[38:42]))
colnames(data_3.7.1_clean)[1] <- "g"
# 3.7.2
data_3.7.2_clean <- na.omit(cbind(as.factor(data_ml3[[1]]), data_ml3[89:94]))
colnames(data_3.7.2_clean)[1] <- "g"
# 3.8.1
# a single measure was reported
# 3.8.2
data_3.8.2_clean <- na.omit(cbind(as.factor(data_ml3[[1]]), data_ml3[29:30])) 
colnames(data_3.8.2_clean)[1] <- "g"

## ML 5
# 5.1.1
data_5.1.1_clean <- cbind(as.factor(data_5.1[[2]]), data_5.1[13:27])
colnames(data_5.1.1_clean)[1] <- "g"
# 5.1.2
data_5.1.2_clean <- cbind(as.factor(data_5.1[[2]]), data_5.1[28:33])
colnames(data_5.1.2_clean)[1] <- "g"
# 5.4
data_5.4_clean <- cbind(as.factor(data_5.4[[1]]), data_5.4[18:41])
colnames(data_5.4_clean)[1] <- "g"
# 5.5.1 & 5.5.2
# from this dataset it appears that this data will be difficult to use.
# 5.5.2
# also difficult to use
# 5.7 
data_5.7_clean <- cbind(as.factor(data_5.7[[3]]), data_5.7[c(25, 34, 35, 36, 37, 38, 39, 40, 41, 42)])
colnames(data_5.7_clean)[1] <- "g"
# 5.9.1
data_5.9.1_clean <- na.omit(cbind(as.factor(data_5.9.1[[4]]), data_5.9.1[c(79, 83, 87, 91, 95, 98, 101)]))
colnames(data_5.9.1_clean)[1] <- "g"

@@

```{r CleaningCodedData, include = FALSE, eval = FALSE}
##### This code can be used to rerun the data preparation to convert the raw 
##### (input) data of the coded data into intermediate data. However, because 
##### the intermediate data is also available in this project, the manuscript  
##### can also be reproduced without running this code block.
# Selecting the relevant rows and columns for the data
coded_data_initial_sel <- coded_data_initial_raw[3:160, 18:57]
coded_data_revised_sel <- coded_data_revised_raw[3:160, 18:38]
coded_data_vignette_raw <- coded_data_vignette_raw[3:160, 2]

@@

```{r FinalPreparationData, include = FALSE, eval = FALSE}
##### This code can be used to rerun the data preparation to convert the 
##### intermediate data into the analysis data. However, because the analysis
##### data is also available in this project, the manuscript can also be 
##### reproduced without running this code block.
### this code prepares the various pieces of data to be ready to use for the 
### analyses.
## confirmatory analyses
# for hypotheses 4, 5, & 6
data_h456_original <- data_prep_h456(coded_data_original_shortened)
data_h456_replications <- data_prep_h456(coded_data_replications)

# for hypotheses 2 and 3
data_h23 <- data_prep_H23(list(data_1.10_clean, data_1.11_clean, 
    data_1.12.3.1_clean, data_1.12.3.2_clean, data_2.12.1_clean, 
    data_2.12.2_clean, data_2.12.3_clean, data_2.15_clean, data_2.20_clean, 
    data_2.23_clean, data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.1_clean,
    data_3.7.2_clean, data_3.8.2_clean, data_5.1.1_clean, data_5.1.2_clean, 
    data_5.7_clean, data_5.9.1_clean), coded_data_replications)

# the averaged across studies version with added information on reported alpha
data_h23_avg <- Data_prep_H23_avg(data_h23, data_h456_original)

## graphs
# plot accompanying the results for Hypotheses 4, 5, & 6.
plot_456_data <- data_prep_plot_456(data_h456_original, data_h456_replications)
# plot accompanying the results for Hypotheses 4, & 6
plot_46_data <- data_prep_plot_46(data_h456_original[c("def_ratio", "op_ratio", "sel_ratio", "quant_ratio", "mod_ratio", "QMP_ratio")], data_h456_replications[c("def_ratio", "op_ratio", "sel_ratio", "quant_ratio", "mod_ratio", "QMP_ratio")])
plot_46_data_rev <- data_prep_plot_46(data_h456_original[c("def_ratio", "op_REV_ratio", "sel_REV_ratio", "quant_REV_ratio", "mod_REV_ratio", "QMP_REV_ratio")], data_h456_replications[c("def_ratio", "op_REV_ratio", "sel_REV_ratio", "quant_REV_ratio", "mod_REV_ratio", "QMP_REV_ratio")])

# plot accompanying the results for Hypotheses 2, & 3
plot_23_data_alpha <- data_prep_plot_23_alpha(data_h23)
plot_23_data_omega <- data_prep_plot_23_omega(data_h23)

### Exporting the final datasets for the analyses
# the open data
open_data(data = data_h456_original, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_h456_original))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_h456_original))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_h456_original))), ".yml"))

open_data(data = data_h456_replications, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_h456_replications))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_h456_replications))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_h456_replications))), ".yml"))

@@

open_data(data = data_h23, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_h23))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_h23))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_h23))), ".yml"))

open_data(data = data_h23_avg, filename = paste0(paste0(
  "Data/AnalysisData/", deparse(substitute(data_h23_avg))), ".csv"),
  codebook = paste0(paste0(
    "Data/AnalysisData/codebook_", 
    deparse(substitute(data_h23_avg))), ".Rmd"),
  value_labels = paste0(paste0(
    "Data/AnalysisData/value_labels_", 
    deparse(substitute(data_h23_avg))), ".yml"))

@@

@@

```{r ReplicationNrTable, warning = FALSE}
# construct the replication ratio table to be printed
replication_nr_table <- data.frame("Many Labs Version" = c("1", "2", "3", "5", "Total"),
                                      "N Total" = c(table(data_h456_replications$many_labs_version), nrow(data_h456_replications)), 
                                      "N Replicated" = c(table(data_h456_replications$many_labs_version, data_h456_replications$hypothesis_support)[, "Yes"], table(data_h456_replications$hypothesis_support)["Yes"]))

@@

Our data had a multilevel structure. Each replication was nested within one of four Many Labs projects. Furthermore, `r sum(data_h456_replications$appearance != 1)` replications used more than one primary measure, resulting in `r nrow(data_h456_replications)` measures in both `r sum(data_h456_replications$appearance == 1)` replications protocols and `r sum(coded_data_original$appearance == 1)` original articles[^2]. Of these `r nrow(data_h456_replications)` measures `r sum(data_h456_replications$mod_check == "True")` were modified from the original to the replication[^3]. In the replications, the data of responses on the measures was further nested in several labs per replication. The combined sample size of all labs in the replications was on average `r round(mean(data_h456_replications[data_h456_replications$appearance == 1]$N), 0)` which was approximately `r round(mean(data_h456_replications[data_h456_replications$appearance == 1]$N) / mean(data_h456_original[data_h456_original$appearance == 1 & !is.na(data_h456_original$N),]$N), 0)` times larger than the average in original studies, which were conducted in single labs.

@@

The average calculated Cronbach's alpha coefficient across replication sets was `r apa_num(mean(data_h23$alpha), digits = 3)` with a standard deviation of `r apa_num(sd(data_h23$alpha, na.rm = TRUE), digits = 3)`. Figure \@ref(fig:Plot23AlphaCode) displays the distributions of the calculated Cronbach’s Alpha scores from each lab for each measure, separated by successful and unsuccessful replication.

```{r ReorderPlot23Data, warning = FALSE}
# data re-ordering (factor order was not saved in export)
plot_23_data_alpha_reordered <- plot_23_data_alpha
plot_23_data_alpha_reordered$g <- fct_inorder(as.factor(plot_23_data_alpha$g), ordered = NA)

data_h23_avg$graph_index <- NA
# adding an index to which row in the plot data the row in data_h23_avg belongs to
for (i in 1:nrow(data_h23_avg)){
  data_h23_avg$graph_index[which(unique(plot_23_data_alpha_reordered$g)[i] == data_h23_avg$g)] <- i
}
```

@@

@@

  # adding the blue triangles for reported reliability and green prediction intervals
  geom_point(data = data_h23_avg, mapping = aes(x = coefficient_reported, y = graph_index), color = "blue", shape = 17, size = 3) +
  geom_point(mapping = aes(x = pi.lb), color = "green", shape = 124, size = 2.5) + 
  geom_point(mapping = aes(x = pi.ub), color = "green", shape = 124, size = 2.5) +

@@

```{r ReportedReliabiltiesRetrieval}
N_reported_reliabilities_original <- sum(data_h456_original$reliability_type != "Not Reported" & data_h456_original$reliability_type != "")

N_reported_reliabilities_replications <- apa_num(sum(data_h456_replications$reliability_type != "Not Reported" & data_h456_replications$reliability_type != ""), numerals = FALSE)

N_reported_reliabilities_replications_number_style <- apa_num(sum(data_h456_replications$reliability_type != "Not Reported" & data_h456_replications$reliability_type != ""))
```

@@

```{r Hypothesis3MainTest, include = FALSE}
## The main model to test hypothesis 3, through a logistic regression model.
H3_test_main_alpha <- glm(formula = replication_success ~ 1 + alpha, 
                                 family = binomial(), data = data_h23_avg)

@@

# well this OR is quite a ridiculous number..., but then again a step from 0 alpha to 1 is quite a jump too...

### rerunning the analyses but now with a standardized alpha value
# transforming the alpha variable 
scaled_alpha <- scale(data_h23_avg$alpha)
scaled_alpha

# rerunning the model with the transformed alpha variable Nr.2
H3_test_interpretable_alpha <- glm(formula = data_h23_avg$replication_success ~ 1 + scaled_alpha, family = binomial())

H3_test_result_interpretable_alpha <- apa_print(H3_test_interpretable_alpha)
